Impacts of the exclusion of scientific surveys from closed areas on population indices, stock assessment, and conservation

### 2022-01-11 paper/paper.Rmd
add notes on bias and trends

- RE: relative error; $(\hat{\theta}_t - \theta_t) / \theta_t$, where $\hat{\theta}_t$ represents the index estimate from the restricted model in year $t$ and $\theta$ represents the index estimate from the full survey set.

@@

- Change in CV ratio over time:

@@

```{r, out.width="\\textwidth", fig.cap="The relationship between the slope of CV ratio through time and the change in the proportion of a species' abundance or biomass estimated to be inside the restricted areas for each survey. The top left quadrant contains species that ... The bottom right quadrant contains species that..."}
include_graphics(here("figs/explore-all-slopes.pdf"))
```

>>>>

- RE: relative error; $(\hat{\theta}_t - \theta_t) / \theta_t$, where $\hat{\theta}_t$ represents the index estimate from the restricted model in year $t$ and $\theta$ represents the index estimate from the full survey set. 
All index estimates were first scaled to their geometric mean across years.

@@

- Change in RE over time: To assess bias, we calculated the slope of a linear regression of RE by year.

@@

```{r, out.width="\\textwidth", fig.cap="The direction of bias, as estimated by the slope of relative error (RE) through time, is related to change in the proportion of a species' abundance or biomass inside the restricted areas. Most surveys tended to have a positive trend in RE (restricted survey indices estimating higher abundance than the status quo) if the proportion inside restricted areas was declining (top left quadrant) or a negative trend in RE (restricted survey indices estimating a trend toward lower abundance than the status quo) when the proportion inside restricted areas was declining (bottom right quadrant)."}
include_graphics(here("figs/explore-all-slopes.pdf"))
```
